\includegraphics[width=1.0\textwidth]{SimAUDLogo.png}\\\quad\\A Three-Tier Architecture Visual-Programming Platform for Building-Lifecycle Data Management

### 2020-03-29 paper_LateX/main.tex
Updates from Overleaf

The emergence of the Internet of Things (IoT) devices has enabled a massive amount of data, which posed some challenges. The data collected during the last two decades exceeded that which has ever been collected in history\cite{Ramaswamy2015InternetReview}. Two significant challenges, other than the availability of data, are to be addressed. On the one hand, managing this big data: transferring, storing, preprocessing, wrangling and mining, optimization, and control in a robust cyber-infrastructure. This lead to cloud computing or ubiquitous computing, that is, computing data in place, without paying much effort in transferring data to local storage/processing machines using scalable storage and computational power on demand maintained by professionals \cite{MellTheTechnology,Bhardwaj2010CLOUDIAAS,Dillon2010CloudChallenges}. On the other hand, delivering useful information to different stakeholders based on their use is yet another challenge.

% Making use of this massive amount of data from the built environment requires 
"Data is not information; data must be presented in a usable form before it becomes information" \cite[p.134]{Reen1996UsabilityFramework}. Raw data from the built environment varies in its degree of usefulness to different stakeholders (actors). "Usability" is different for different stakeholders. For instance, A Building Energy Modeller (BEM) requires data such as Green Building eXtensible Markup Language (gbXML) \cite{GbXMLSchema}, schedules of operations, set-points, number of occupants,etc.. At the same time, a Facility Manager (FM) would be more interested in reducing maintenance costs by fault detection and diagnostics (FDD)\cite{Zibion2018DevelopmentInformation} algorithms and dashboards. This difference in uses requires users with proper domain knowledge alongside with programming or procedural thinking skills for automating, prototyping, analyzing, building work-flows using the big data and IoT sensors. At the same time, they do not need to be professional programmers, but rather End-use programmers.

The term \textit{End-use programmer} (or Novice developer) first introduced by \cite{Nardi1993AComputing} is used to describe non-professionals without programming and code structures knowledge \cite{MARGARETM.BURNETTANDCHRISTOPHERSCAFFIDIEnd-UserEd.}. Most programs today are written by novice programmers \cite{Rothermel2011TheEngineering} who use spreadsheets, writing add-ons/plugins to support their work or add functionality to the software, running MATLAB simulations \cite{MATLABSimulink}, writing python codes, or IPython notebooks \cite{ScaffidiEstimatingProgrammers}. The main difference between the end-user developer and the professional developer is the goal of the development. The former writes a program focusing on getting tasks done without paying attention to debugging, unit-testing, or re-usability. However, the latter develops, maintain, debug, and test a robust software for others to use\cite{LiebermanEnd-userDevelopment}. End-use development mostly involves modifying or extending a software artifact (known as programming by example, or programming by demonstration). For example, \textit{Extended annotation or parameterization}: whereas a user can define a new functionality by selecting a readily developed set of functions by other users and stored in shared repositories \cite{Lieberman2006End-UserParadigm}. To make this task handy to end-use programmers, a proper programming notation should be utilized.

@@

Visual Programming Language (VPL), also known as box-and-wire programming or data-flow programming utilizes user-friendly graphical elements to display the flow of data between different components (Figure \ref{fig:vpl_example}). To date, there has been little agreement on the superiority of visual programming languages (VPLs) over the textual programming languages (TPLs). Green et.al. \cite{PDFConjecture} and Moher et.al. \cite{Moher1993ComparingPrograms} adopted this stance. However, \cite{MENZIES2002EVALUATIONLANGUAGES} argued that VPLs could be significantly useful in motivating beginners to learn to program as they are informative in the sense of spatial reasoning and ideas generation. However, he argued that those advantages are not generalized and should not be isolated from the task being studied. Also, TPL is more productive in terms of large-scale and complex software development tasks. There is no conclusive evidence of the superiority of one over the other. Thus, a hybrid VPL/TPL is proven to be suitable amongst users. Many software enables this type of scripting which gained wide popularity such as Rhinoceros VPL Grasshopper\cite{Bachman2017Grasshopper:3D,2011bGrasshopperRhino} whose user-community extended its limits by contributing to developing TPL based functions amongst others for building and urban simulation \cite{RoudsariLadybug:Design, PeronatoIntegratingCitySim,Koltsova2011ComponentsGeometry}, daylight analysis \cite{JakubiecDIVAENERGYPLUS,LagiosANIMATEDRADIANCE/DAYSIM}, Machine learning\cite{Abdelrahman2017EnhancingLanguage,Abdelrahman2019ANT:Development}.

\hl{This research addresses two primary problems:}
\begin{enumerate}
    \item \hl{Managing buildings' big data requires flexibility and scalability.}
    %Maybe a better problem the VP addresses is the ability to connect data to mode
    \item \hl{Different users are use data differently.}
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=0.9\columnwidth]{imgs/vpl_example.png}
\caption{\hl{A screenshot from our platform indicating a parametric simulation process on the cloud using (BuildSimHub)}. The figure is an example of Visual programming Language (also known as box-and-wire programming notation, and data-flow programming) where blocks of code functions are encapsulated in the boxes (known as components), while data flows from one or more component output variable to other component input variable. A component can hold as many inputs as needed, while the code behind each component follows a specific schema. Some components are used only as input components such as "file, numerical, panel" and some components work as output visualizations such as "panel, 3d visualization canvas, plotting components .."}
\label{fig:vpl_example}
\end{figure}
We introduce a Three-tier architecture web platform as a resolution to these problems. The objectives of this research are: (1) Making IoT data from the built environment useful to different stakeholders, (2) An Open platform for developing and sharing different models amongst end-use programmers. (3) Provide flexibility and scalability by separating the platform into three distributed layers. The rest of the paper is structured as follows: In section \ref{section1}, we explain the three-tier architecture. The components of the three-tier architecture are explained in details in the subsequent sections \ref{section3} (Actors), \ref{sec:presentationLayer} (Presentation Layer), \ref{sec:applicationlayer} (Application Layer), and \ref{sec:datalayer} (Data Layer).

\section{Three-Tier Architecture}
\label{section1}
\textit{Three-tier architecture} is a client-server software architecture pattern that has several potentials in distribution applications \cite{Booch1994OBJECT-ORIENTEDEDITION}. The key aspect of this architecture is that it enables the reusability of program building blocks (also referred to as components) such as sharing software components at run time, replicating the same component, controlled adaptation of code, or independent adaptation of components \cite{Taylor1998ThePerspective,Wijegunaratne1998DistributedEngineering}. This pattern consists of three functionally separated layers \cite{Schuldt2017Multi-tierArchitecture} (Figure \ref{fig:figure1}), those are: \textbf{1) Presentation layer} (the client-side), \textbf{2) Application layer} (also known as business logic, controllers and process management layer), and \textbf{3) Data layer} (also known as data storage). The presentation layer constitutes the user-interface side of the application. All human-computer interactions (HCI) happen on this layer. On the other side, the Business logic layer consists of the core engine where component functions that carry out the workload by receiving requests from the presentation layer get the relevant data from the Data layer and process this data then, sends back the response to the presentation layer. Finally, the Data layer consists of data querying (acquire from a data source), storage (stored in the relational database on a local server), and accessing (feed to the user). Each of these three tires is discussed in detail in the subsequent sections.

@@

@@

\section{actors}
\label{section3}
We use the term "Actor" to refer to different users/stakeholders within the built environment. "Usability" is the critical factor in obtaining "information" from data. Data obtained from the built environment does not hold equal usefulness for all stakeholders. Furthermore, in its raw format, IoT data consists of many problems, including noise, missing data, non-valid data, ill-labeled data points, duplicates, and non-standardized IoT representation. These problems should be dealt with before delivering this data to non-expert users. \hl{We define some actors or stakeholders who are involved in the building's life cycle energy modeling and data analysis and their corresponding data usage based on a systematic review conducted by Zou et.al \cite{Zou2018ReviewPerspectives} of 10 years publications till 2017 and  using Natural language processing (NLP) \cite{Abdelrahman2020BuildingWord-Embeddings}.

@@

Then, we identified three main data-related actions, namely, \textbf{End-use programming}, \textbf{Data monitoring}, and \textbf{Data input}. Different stakeholders are clustered based on these three activities (Figure \ref{fig:figure6}). Then, these activities are reflected in the presentation layer \textit{(explained in section \ref{sec:presentationLayer})}  as three major components: 1) Hybrid VPL/TPL interface, 2) Interactive, shareable, embedded dashboards, and 3) Shareable, embedded forms. The interface of the platform is shown in figure \ref{fig:platformInterface}.}

@@

\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{imgs/tpl_interface.png}
\caption{TPL interface using Python script. The python script enables reading, writing inputs and outputs of different components, as well as adding pre/post processing functions to the inputs/outputs.}
\label{fig:tpl_interface}
\end{figure*}
\subsection{Dashboard and forms}

\label{sec:applicationlayer}
The dashboard and forms are located in the same tab called 'Dashboard'. It is an information management tool directed to stakeholders who are not involved directly in the development of the project i.e., to track performance, metrics, and other key data points; or to get feedback and other user inputs (questionnaires or thermal comfort feedback). The project owner does the design of the dashboard, using the input components (e.g., numeric slider, optionList, listView, RadioButtons, and  Panels ) and the output components (e.g., Panels, Plots, 3D views, 2D plans, images, videos etc.). Then, the dashboard could be shared with public or specific people to view or interact. It can also be embedded within other websites.
\section{Application Layer}
The application layer receives the deep function requests from the presentation layer in the form of a JSON object following specific schema. On the one hand, If there are data-related processes, it sends a request to the data layer (explained in detail in section \ref{sec:datalayer}. On the other hand, if there are no database-related processes, the JSON object consisted of the inputs and the component function callback. The function then starts to operate in three cases:
\begin{enumerate}
    \item It runs the function directly from the node. 
    \item It starts other cloud engines to run the functions. 
    \item It uses third party engines (e.g. BuildSimHub) to perform the operation. 
\end{enumerate}
Consequently, the function response back to the presentation layer as a JSON object with the outputs (if any), Errors, and logs. The response JSON object also follows a predefined schema as shown in figure \ref{fig:component}. The whole process is illustrated in figure \ref{fig:structure} (steps: 1, 2, 3, 8, 9).
\begin{figure*}[ht]
\centering
\includegraphics[width=\linewidth]{imgs/allStructure.png}
\caption{This figure shows the flow of data within the three tiers: (1) The actor interact with the presentation layer three ways: programming, viewing dashboards, or giving feedback; (2)The user interaction results in sending requests to the application layer to be processed; (3)The application layer starts processing inputs and relevant functions; (4) If there is any required data from the databases, a QUERY is sent to the data layer; (5) then, the data layer respond with the corresponding data from different databases (6,7); (8) The application layer then runs the required components using the distributed engines; (9) The output of step (7) is responded back to the presentation layer along with the logs/errors in JSON format. higher resolution image can be downloaded \href{https://user-images.githubusercontent.com/6969514/72152397-cee71700-33e5-11ea-9108-c6823d2be504.png}{here}
}
\label{fig:structure}
\end{figure*}

@@

The metadata and models are either input by the users through the presentation layer or assigned by the application layer. These data are mainly text. Once passed to the data layer, they are static and stored in the relational databases (Figure \ref{fig:relationDatabase}). As for the building operational data, the time series data comes from servers of different Building Management Systems. BMS in different buildings are various, in terms of data structure, sampling rate, communication protocol, etc., making data querying a troublesome task. The platform dealt with this by deploying the PI system from OSIsoft \cite{PiSystem}, which queries data from different types of servers, such as BACnet (Building Automation and Control networks) and OPC (Open Platform Communications), and stores the compressed data on the local server.\par
\begin{figure*}
\includegraphics[width=\linewidth]{imgs/uml_relationship.jpeg}
\caption{Relational database: A higher resolution image can be downloaded  \href{https://user-images.githubusercontent.com/6969514/72235771-e9e89f80-360e-11ea-9cf7-91c0f521576c.jpeg}{here}
}
\label{fig:relationDatabase}
\end{figure*}
Data exchange between the application layer and the data layer is done through RESTful API and mainly in JSON format. For example, if a user wants to see the energy consumption trend of a building, he/she will select the data point and define the time period in VPL canvas. The deep functions in the application layer will get the information and accordingly send the request. The API will retrieve data from the server and send it back as a JSON file, which will then be plotted in the canvas.
\section{Case study} \label{section:casestudy}
In this section, we introduce a case-study to evaluate our platform.

@@

\section*{ACKNOWLEDGMENTS}
% This paper is a part of a project funded by the Ng Teng Fong Charitable Foundation (NTFCF) research funding.
\clearpage
\balance

@@

\bibliography{references.bib,./references2.bib,SampleReferences.bib}
\end{document}

>>>>

The emergence of the Internet of Things (IoT) devices has enabled a massive amount of data, which posed some challenges. The data collected during the last two decades exceeded that which has ever been collected in history\cite{Ramaswamy2015InternetReview}. Two significant challenges, other than the availability of data, are to be addressed. On the one hand, managing this big data: transferring, storing, preprocessing, wrangling and mining, optimization, and control in a robust cyber-infrastructure. This lead to cloud computing or ubiquitous computing, that is, computing data in place, without paying much effort in transferring data to local storage/processing machines using scalable storage and computational power on demand maintained by professionals \cite{MellTheTechnology,Bhardwaj2010Cloud,Dillon2010CloudChallenges}. On the other hand, delivering useful information to different stakeholders based on their use is yet another challenge.

% Making use of this massive amount of data from the built environment requires 
"Data is not information; data must be presented in a usable form before it becomes information" \cite[p.134]{Reen1996UsabilityFramework}. Raw data from the built environment varies in its degree of usefulness to different stakeholders (actors). "Usability" is different for different stakeholders. For instance, A Building Energy Modeller (BEM) requires data such as Green Building eXtensible Markup Language (gbXML) \cite{GreenBuildingXMLgbXMLSchema2019GbXMLSchema}, schedules of operations, set-points, number of occupants,etc.. At the same time, a Facility Manager (FM) would be more interested in reducing maintenance costs by fault detection and diagnostics (FDD)\cite{Zibion2018DevelopmentInformation} algorithms and dashboards. This difference in uses requires users with proper domain knowledge alongside with programming or procedural thinking skills for automating, prototyping, analyzing, building work-flows using the big data and IoT sensors. At the same time, they do not need to be professional programmers, but rather End-use programmers.

The term \textit{End-use programmer} (or Novice developer) first introduced by \cite{Nardi1993AComputing} is used to describe non-professionals without programming and code structures knowledge \cite{InteractionDesignFoundation2014End-UserEd.}. Most programs today are written by novice programmers \cite{Rothermel2011TheEngineering} who use spreadsheets, writing add-ons/plugins to support their work or add functionality to the software, running MATLAB simulations \cite{Mathworks2016MATLABSimulink}, writing python codes, or IPython notebooks \cite{ScaffidiEstimatingProgrammers}. The main difference between the end-user developer and the professional developer is the goal of the development. The former writes a program focusing on getting tasks done without paying attention to debugging, unit-testing, or re-usability. However, the latter develops, maintain, debug, and test a robust software for others to use\cite{LiebermanEnd-userDevelopment}. End-use development mostly involves modifying or extending a software artifact (known as programming by example, or programming by demonstration). For example, \textit{Extended annotation or parameterization}: whereas a user can define a new functionality by selecting a readily developed set of functions by other users and stored in shared repositories \cite{Lieberman2006End-UserParadigm}. To make this task handy to end-use programmers, a proper programming notation should be utilized.

@@

Visual Programming Language (VPL), also known as box-and-wire programming or data-flow programming utilizes user-friendly graphical elements to display the flow of data between different components (Figure \ref{fig:vpl_example}). To date, there has been little agreement on the superiority of visual programming languages (VPLs) over the textual programming languages (TPLs). Green et.al. \cite{Green1991ComprehensibilityConjecture} and Moher et.al. \cite{Moher1993ComparingPrograms} adopted this stance. However, \cite{MENZIES2002EVALUATIONLANGUAGES} argued that VPLs could be significantly useful in motivating beginners to learn to program as they are informative in the sense of spatial reasoning and ideas generation. However, he argued that those advantages are not generalized and should not be isolated from the task being studied. Also, TPL is more productive in terms of large-scale and complex software development tasks. There is no conclusive evidence of the superiority of one over the other. Thus, a hybrid VPL/TPL is proven to be suitable amongst users. Many software enables this type of scripting which gained wide popularity such as Rhinoceros VPL Grasshopper\cite{Bachman2017Grasshopper:3D,McNeel2010GrasshopperRhino} whose user-community extended its limits by contributing to developing TPL based functions amongst others for building and urban simulation \cite{RoudsariLadybug:Design, PeronatoIntegratingCitySim,Koltsova2011ComponentsGeometry}, daylight analysis \cite{Jakubiec2011DIVAEnergyPlus,Lagios2010AnimatedDaysim}, Machine learning\cite{Abdelrahman2017EnhancingLanguage,AbdelRahman2017GH_CPython:Grasshopper,Abdelrahman2019ANT:Development}.

This research addresses two primary problems:
\begin{enumerate}
    \item Managing buildings' big data requires flexibility and scalability.
    %Maybe a better problem the VP addresses is the ability to connect data to mode
    \item Different users use data differently.
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=0.9\columnwidth]{imgs/vpl_example.png}
\caption{A screenshot from our platform indicating a parametric simulation process on the cloud using (BuildSimHub). The figure is an example of Visual programming Language (also known as box-and-wire programming notation, and data-flow programming) where blocks of code functions are encapsulated in the boxes (known as components), while data flows from one or more component output variable to other component input variable. A component can hold as many inputs as needed, while the code behind each component follows a specific schema. Some components are used only as input components such as "file, numerical, panel" and some components work as output visualizations such as "panel, 3d visualization canvas, plotting components .."}
\label{fig:vpl_example}
\end{figure}
We introduce a Three-tier architecture web platform as a resolution to these problems. The objectives of this research are: (1) Making IoT data from the built environment useful to different stakeholders, (2) An Open platform for developing and sharing different models amongst end-use programmers. (3) Provide flexibility and scalability by separating the platform into three distributed layers. The rest of the paper is structured as follows: In section \ref{section1}, we explain the three-tier architecture. The components of the three-tier architecture are explained in details in the subsequent sections \ref{section3} (Actors), \ref{sec:presentationLayer} (Presentation Layer), \ref{sec:applicationlayer} (Application Layer), and \ref{sec:datalayer} (Data Layer).

\section{Three-Tier Architecture}
\label{section1}
\textit{Three-tier architecture} is a client-server software architecture pattern that has several potentials in distribution applications \cite{Booch2008Object-orientedEdition}. The key aspect of this architecture is that it enables the reusability of program building blocks (also referred to as components) such as sharing software components at run time, replicating the same component, controlled adaptation of code, or independent adaptation of components \cite{Taylor1998ThePerspective,Wijegunaratne1998DistributedEngineering}. This pattern consists of three functionally separated layers \cite{Schuldt2017Multi-tierArchitecture} (Figure \ref{fig:figure1}), those are: \textbf{1) Presentation layer} (the client-side), \textbf{2) Application layer} (also known as business logic, controllers and process management layer), and \textbf{3) Data layer} (also known as data storage). The presentation layer constitutes the user-interface side of the application. All human-computer interactions (HCI) happen on this layer. On the other side, the Business logic layer consists of the core engine where component functions that carry out the workload by receiving requests from the presentation layer get the relevant data from the Data layer and process this data then, sends back the response to the presentation layer. Finally, the Data layer consists of data querying (acquire from a data source), storage (stored in the relational database on a local server), and accessing (feed to the user). Each of these three tires is discussed in detail in the subsequent sections. A summarized workflow is illustrated in figure \ref{fig:structure}.

@@

\begin{figure*}[ht]
\centering
\includegraphics[width=0.8\linewidth]{imgs/allStructure.png}
\caption{This figure shows the flow of data within the three tiers: (1) The actor interact with the presentation layer three ways: programming, viewing dashboards, or giving feedback; (2)The user interaction results in sending requests to the application layer to be processed; (3)The application layer starts processing inputs and relevant functions; (4) If there is any required data from the databases, a QUERY is sent to the data layer; (5) then, the data layer respond with the corresponding data from different databases (6,7); (8) The application layer then runs the required components using the distributed engines; (9) The output of step (7) is responded back to the presentation layer along with the logs/errors in JSON format. higher resolution image can be downloaded \href{https://user-images.githubusercontent.com/6969514/72152397-cee71700-33e5-11ea-9108-c6823d2be504.png}{here}
}
\label{fig:structure}
\end{figure*}

@@

\section{actors}
\label{section3}
We use the term "Actor" to refer to different users/stakeholders within the built environment. "Usability" is the critical factor in obtaining "information" from data. Data obtained from the built environment does not hold equal usefulness for all stakeholders. Furthermore, in its raw format, IoT data consists of many problems, including noise, missing data, non-valid data, ill-labeled data points, duplicates, and non-standardized IoT representation. These problems should be dealt with before delivering this data to non-expert users. We define some actors or stakeholders who are involved in the building's life cycle energy modeling and data analysis and their corresponding data usage based on a systematic review conducted by Zou et.al \cite{Zou2018ReviewPerspectives} of 10 years publications till 2017 and  using Natural language processing (NLP) \cite{Abdelrahman2020BuildingWord-Embeddings}.

@@

Then, we identified three main data-related actions, namely, \textbf{End-use programming}, \textbf{Data monitoring}, and \textbf{Data input}. Different stakeholders are clustered based on these three activities (Figure \ref{fig:figure6}). Then, these activities are reflected in the presentation layer \textit{(explained in section \ref{sec:presentationLayer})}  as three major components: 1) Hybrid VPL/TPL interface, 2) Interactive, shareable, embedded dashboards, and 3) Shareable, embedded forms. The interface of the platform is shown in figure \ref{fig:platformInterface}.

@@

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{imgs/tpl_interface.png}
\caption{TPL interface using Python script. The python script enables reading, writing inputs and outputs of different components, as well as adding pre/post processing functions to the inputs/outputs.}
\label{fig:tpl_interface}
\end{figure}
\subsection{Dashboard and forms}

\label{sec:applicationlayer}
The dashboard and forms are located in the same tab called 'Dashboard'. It is an information management tool directed to stakeholders who are not involved directly in the development of the project i.e., to track performance, metrics, and other key data points; or to get feedback and other user inputs (questionnaires or thermal comfort feedback). The project owner does the design of the dashboard, using the input components (e.g., numeric slider, optionList, listView, RadioButtons, and  Panels ) and the output components (e.g., Panels, Plots, 3D views, 2D plans, images, videos etc.). Then, the dashboard could be shared with public or specific people to view or interact. It can also be embedded within other websites.
\section{Application Layer}
The application layer receives the deep function requests from the presentation layer in the form of a JSON object following specific schema. On the one hand, If there are data-related processes, it sends a request to the data layer (explained in detail in section \ref{sec:datalayer}. On the other hand, if there are no database-related processes, the JSON object consisted of the inputs and the component function callback. The function then starts to operate in three cases:
\begin{enumerate}
    \item It runs the function directly from the node. 
    \item It starts other cloud engines to run the functions. 
    \item It uses third party engines (e.g. BuildSimHub) to perform the operation. 
\end{enumerate}
Consequently, the function response back to the presentation layer as a JSON object with the outputs (if any), Errors, and logs. The response JSON object also follows a predefined schema as shown in figure \ref{fig:component}. The whole process is illustrated in figure \ref{fig:structure} (steps: 1, 2, 3, 8, 9).

@@

The metadata and models are either input by the users through the presentation layer or assigned by the application layer. These data are mainly text. Once passed to the data layer, they are static and stored in the relational databases (Figure \ref{fig:relationDatabase}). As for the building operational data, the time series data comes from servers of different Building Management Systems. BMS in different buildings are various, in terms of data structure, sampling rate, communication protocol, etc., making data querying a troublesome task. The platform dealt with this by deploying the PI system from OSIsoft, which queries data from different types of servers, such as BACnet (Building Automation and Control networks) and OPC (Open Platform Communications), and stores the compressed data on the local server.\par
\begin{figure}
\includegraphics[width=\columnwidth]{imgs/uml_relationship.jpeg}
\caption{Relational database: A higher resolution image can be downloaded  \href{https://user-images.githubusercontent.com/6969514/72235771-e9e89f80-360e-11ea-9cf7-91c0f521576c.jpeg}{here}. 
}
\label{fig:relationDatabase}
\end{figure}
Data exchange between the application layer and the data layer is done through RESTful API and mainly in JSON format. For example, if a user wants to see the energy consumption trend of a building, he/she will select the data point and define the time period in VPL canvas. The deep functions in the application layer will get the information and accordingly send the request. The API will retrieve data from the server and send it back as a JSON file, which will then be plotted in the canvas.

\section{Use case scenario} \label{section:casestudy}
In this section, we introduce a use case based on Cockburn's template \cite{Cockburn1998UseTemplate}  to illustrate how the platform works. The use case is a parametric energy simulation of a small office building from ANSI/ASHRAE/IES Standard 90.1 commercial reference buildings \cite{Field2010UsingStudies} shown in figure \ref{fig:commrefbuild}.

\begin{figure}[h]
\includegraphics[width=\columnwidth]{paper_LateX/imgs/comm_ref_build.png}
\caption{One of the reference buildings developed by the U.S. Department of Energy (DOE). The building represents a small office with 5,500 square feet area and one floor. The image is a screenshot taken from the embedded 3d viewer in our platform, and provided by BuildSimHub (in the application layer). an animated GIF of the 3d-viewer could be viewed \href{https://user-images.githubusercontent.com/6969514/77833696-3eb1a600-717a-11ea-8f77-475be6d57cfb.gif}{here}}
\label{fig:commrefbuild}
\end{figure}
\textbf{USE CASE:1 Conduct a Parametric Energy Simulation}\\
- - - - - - - - - - - - - - - - - - - - - - - - - - - \\
CHARACTERISTIC INFORMATION\\
\textbf{\underline{Context of use:}} EnergyModeller conducts a parametric building energy simulation of a small office building using the three-tier architecture platform.\\
\textbf{\underline{Scope:}} Platform\\
\textbf{\underline{Level:}} Summary\\
\textbf{\underline{Preconditions:}} The user must have a valid authentication to the platform and a supported web browser (e.g. Google Chrome).\\
\textbf{\underline{Actor(s):}} EnergyModeller, BuildSimHub (cloud simulation engine).\\
\textbf{\underline{Trigger:}} Firstly, the EnergyModeller should start a new project. Secondly, IDF file of the EnergyPlus model of version greater than 8.0.

\underline{Description: }
\begin{enumerate}
    \item EnergyModeller starts a new definition (project).
    \item The IDF file link and global unique id (GUID) are retrieved. 
    \item EnergyModeller uploads the IDF file to the data layer (a scalable google cloud bucket) using a file upload component (Figure \ref{fig:fileupload_comp}) -- an animated GIF image could be viewed \href{https://user-images.githubusercontent.com/6969514/77833649-16c24280-717a-11ea-9df1-8a5e0f7bae83.gif}{here}.

    \item EnergyModeller loads a "buildSimHub Parametric Study" component (Figure \ref{fig:parametric_study}). 
    \item fsdfsafasdf
    \item fsdfsafasdf
    \item fsdfsafasdf
\end{enumerate}

\begin{figure}[h]
\includegraphics[width=\columnwidth]{paper_LateX/imgs/file_compo.png}
\caption{ File upload component in the presentation layer: a) The user is prompted to select a file. The file is uploaded to a google cloud bucket; b) Then, the file could be triggered by its global unique id}
\label{fig:fileupload_comp}
\end{figure}

@@

\section*{ACKNOWLEDGMENTS}
% This paper is a part of a project funded by the Ng Teng Fong Charitable Foundation (NTFCF) research funding.
% \clearpage
% \balance

@@

\bibliography{references.bib,references2.bib}
\end{document}
